\TheTitle

### 2017-07-03 paper/results.tex
Results: Description of accuracy and timing

@@

@@

@@

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q5.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for answering how
  many authors were involved with a merge tree.}
  \label{fig:q5_accuracy}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q5.pdf}
  \caption{Time comparison between Gitk and \tool, for answering how
  many authors were involved with a merge tree.}
  \label{fig:q5_timing}
\end{figure}

@@

\subsubsection{How many files were modified in this merge tree}
\label{ssub:how_many_files_were_modified_in_this_merge_tree}

@@

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q8.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for answering
    which file had the most changes.}
  \label{fig:q8_accuracy}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q8.pdf}
  \caption{Time comparison between Gitk and \tool, for answering which
    file had the most changes.}
  \label{fig:q8_timing}
\end{figure}

@@

% Figure~\ref{fig:q9_accuracy}

>>>>

There is almost no variation in accuracy between participants using
\tool, while there is more variance in Gitk. There were two outliers
among the instances using \tool, which lie within the second and third
quartiles for the accuracy measure of Gitk. The furthest outlier for
\tool lies at a distance that is slightly greater than the median for
Gitk. We see these results in Figure~\ref{fig:q3_accuracy}.

We similar results for the timing metric in Figure~\ref{fig:q3_timing}.
All significant data occurs within less time than the second, third, and
fourth quartile of the Gitk results. Nearly all outlier instances in
\tool are within the third quartile group of the instances of Gitk with
the exception of the most extreme, which lies in the fourth quartile
group.

@@

Overall, we see that \tool enables users to correctly identify the
series of merges required to merge a given commit more quickly than with
Gitk. Furthermore, the accuracy of incorrect results are closer to being
correct than the incorrect answers for Gitk.

@@

In Figure~\ref{fig:q4_accuracy}, we can see that there is again, very
little variance in the accuracy of results for \tool compared to the
accuracy of the results in Gitk.

In Figure~\ref{fig:q4_timing} there is less variance in the time taken
to come to an answer with \tool than with Gitk. Furthermore, we see that
a majority of the participants were able to complete the task in \tool
in much less time than 50\% of the participants using Gitk.

@@

Overall, participants are able to determine other commits that are
related to a given commit more quickly and more accurately with \tool
than with Gitk.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q5.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for answering how
  many authors are involved with a merge tree.}
  \label{fig:q5_accuracy}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q5.pdf}
  \caption{Time comparison between Gitk and \tool, for answering how
  many authors are involved with a merge tree.}
  \label{fig:q5_timing}
\end{figure}

Again, we see very similar results in Figure~\ref{fig:q5_accuracy} and
Figure~\ref{fig:q5_timing}, to the results found in the previous two
tasks. The variance in accuracy and time taken is much greater with
Gitk than with \tool. This suggests that the participants were able to
determine the number of authors more quickly and with better accuracy
with \tool than Gitk.

@@

We similar results in Figure~\ref{fig:q6_timing} as with the previous
questions. There is greater variance in the time taken for participants
to determine who contributed the most changes to a group of commits
using Gitk than with \tool.

\subsubsection{How many files are modified in this merge tree}
\label{ssub:how_many_files_were_modified_in_this_merge_tree}

@@

Figure~\ref{fig:q7_accuracy} and Figure~\ref{fig:q7_timing} show similar
results, showing that the accuracy and time for the participants to
produce a response was more variable with Gitk than with \tool.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/accuracy/q8.pdf}
  \caption{Accuracy comparison between Gitk and \tool, for answering
    which file(s) had the most changes.}
  \label{fig:q8_accuracy}
\end{figure}

It was possible for this question to have multiple answers. If there
were multiple files with the same number of modifications, in lines of
code changed, then the correct response would be a list of all files
with those changes. Ultimately, we see a fairly clean distribution of
accuracies using Gitk in Figure~\ref{fig:q8_accuracy}, with the median
being one file away from the correct answer. Aside from two outliers,
all responses from the participants using \tool were correct.

We see the same behaviour in Figure~\ref{fig:q8_timing}, showing that
there is more variance in the time taken to respond to the question when
the participant is using Gitk versus when they are using \tool.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/timing/q8.pdf}
  \caption{Time comparison between Gitk and \tool, for answering which
    file(s) had the most changes.}
  \label{fig:q8_timing}
\end{figure}

Overall, we see an improvement in correctness, accuracy, and time taken
to determine which file or files had the most changes in the group of
commits when the participants use \tool over Gitk.

@@

We don't see a tremendous difference in the accuracy performance of the
participants between Gitk and \tool in Figure~\ref{fig:q9_accuracy}.
This is consistent with the results for the correctness metric. Unlike
accuracy and correctness, we see a noticeable difference in the time
performance of the participants between \tool and Gitk
(Figure~\ref{fig:q9_timing}).
